Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/evalrelate.tex
Change format of abstract
minor edits

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traversed this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

We used go vector clocks \cite{vclock} to keep track of vector clocks and also our merge functionality is built on top of this implementation.

>>>>

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traversed this tree and collected informations about locations of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

In this phase we use \texttt{encoding/gob} package to decode data items corresponding to each program point written to the log. We used go vector clocks \cite{vclock} to keep track of vector clocks and also our merge functionality is built on top of this implementation.
